Title

### 2014-01-17 paper/parts/methods.tex
Fixed the explanation of orphans for the interaction-based community.

Since our goal is to explore the functional communities of this network, we filter this network down to the subset of users which actively interact with each other (e.g., retweets and mentions). We do this through a metric we call (incoming/outgoing) information events. We define an outgoing information event for a given user $u$ as either a mention made by $u$ of another user in the network, or if another user in the network retweets a tweet made by $u$. The logic for this definition is as follows, if $u$ mentions a user $v$ this can be thought of as $u$ directly sending information to $v$, and if $u$ is retweeted by $v$ then $v$ received information from $u$ and rebroadcast it to their followers. In either case there was information outgoing from $u$ which affected the network in the some way. Analogously, we define the incoming information event for $u$ as either being mentioned by a different user in the network, or by retweeting another user in the network.
%function and information share is important We then filter down this starting %network to include only users that [[what??]]. To do this 
%Since one of the community types we want to explore is based on the explicit interactions ( between users, we filter the dataset in order to take into account only users who make use of these kinds of features in their tweets. [[Seeems out of place]]
%We define an event of outgoing information for a given user $u$ as either a mention made by $u$ of another user in the network, or a retweet by another user of one of $u$'s tweets. 
%[[Switched the readers perspective]]When we mention someone we are in fact sending him some information, and when we are retweeted it means that the person that retweeted us has received some information from us and is sharing it. 
With (incoming/outgoing) information events defined we filtered the network by eliminating all users with less than 9 outgoing \emph{and} incoming information events, i.e., less than one information event per type per week on average. 
We then further restricted our analysis to the strong giant connected component of the network built from the (incoming/outgoing) information filtered set of users. %and whose link represent a user-follower relationship.
In this study the link is directed from the user to the follower because this is the direction in which the information flows.\textbf{[[Josh: Is this the case for all the analysis or just the transfer entropy?]]} The final network consists of 6,917 nodes and 1,481,131 edges.

>>>>

Since our goal is to explore the functional communities of this network, we filter this network down to the subset of users which actively interact with each other (e.g., retweets and mentions). We do this through a metric we call (incoming/outgoing) information events. We define an outgoing information event for a given user $u$ as either a mention made by $u$ of another user in the network, or if another user in the network retweets a tweet made by $u$. The logic for this definition is as follows, if $u$ mentions a user $v$ this can be thought of as $u$ directly sending information to $v$, and if $u$ is retweeted by $v$ then $v$ received information from $u$ and rebroadcast it to their followers. In either case there was information outgoing from $u$ which affected the network in the some way. Analogously, we define the incoming information event for $u$ as either being mentioned by a different user in the network, or by retweeting another user in the network.
%function and information share is important We then filter down this starting %network to include only users that [[what??]]. To do this 
%Since one of the community types we want to explore is based on the explicit interactions ( between users, we filter the dataset in order to take into account only users who make use of these kinds of features in their tweets. [[Seeems out of place]]
%We define an event of outgoing information for a given user $u$ as either a mention made by $u$ of another user in the network, or a retweet by another user of one of $u$'s tweets. 
%[[Switched the readers perspective]]When we mention someone we are in fact sending him some information, and when we are retweeted it means that the person that retweeted us has received some information from us and is sharing it. 
With (incoming/outgoing) information events defined we filtered the network by eliminating all users with less than 9 outgoing \emph{and} incoming information events, i.e., less than one information event per type per week on average. 
We then further restricted our analysis to the strong giant connected component of the network built from the (incoming/outgoing) information filtered set of users. %and whose link represent a user-follower relationship.
In this study the link is directed from the user to the follower because this is the direction in which the information (in the case of transfer entropy) or influence (in the case of mention-retweets) flows. The final network consists of 6,917 nodes and 1,481,131 edges.

### 2014-01-17 paper/parts/results.tex
Fixed the explanation of orphans for the interaction-based community.

The number of singletons by community type is also shown in Table~\ref{Table-comm_count}. We see that the topic- and interaction-based communities have the most singletons, with the activity-based community dominating this measure. This result for the activity-based community is an artifact of a property of the retweet/mention weighting: 717 of the users were removed in the process \textbf{TK: Fix after clarification from Elisa}.

@@

\begin{figure}[ht]
  \centering
\includegraphics[width=0.50\textwidth]{figures/comm0_labels-mention-retweet_weights-hashtag-ecdf.pdf}
\caption{The proportion of edges with a weight at least as large as the weight on the horizontal axis, across the types of edges described in Figure~\ref{Fig-edge_types}. The community is defined by user interactions, and the edge weights are determined by topic similarity. The dashed horizontal lines indicate the median weight for each type of edge. Note the logarithmic scale on the horizontal axis.}
\label{Fig-dist_across_community}
\end{figure}

>>>>

The number of singletons by community type is also shown in Table~\ref{Table-comm_count}. We see that the topic- and interaction-based communities have the most singletons, with the activity-based community dominating this measure. This result for the activity-based community is partially an artifact of a property of the retweet/mention weighting: 717 of the users were disconnected from the network by how the weights were defined, resulting in `orphan' nodes which we have included in the collection of singletons for all of our analyses. However, even after accounting for this artifact, the interaction-based network still has the most non-orphan singletons. This seems to indicate that a large fraction of the 6917 (nearly 25\%) do not interact with each other in a concerted way that would mark them as a community under our interaction-based definition.

@@

\begin{figure}[ht]
  \centering
\includegraphics[width=0.50\textwidth]{figures/comm0_labels-mention-retweet_weights-hashtag-ecdf.pdf}
\caption{The proportion of edges with a weight at least as large as the weight on the horizontal axis, across the types of edges described in Figure~\ref{Fig-edge_types}. The community is defined by user interactions, and the edge weights are determined by topic similarity. The dashed vertical lines indicate the median weight for each type of edge. Note the logarithmic scale on the horizontal axis.}
\label{Fig-dist_across_community}
\end{figure}
